Grand Prix motorcycle racing

### 2021-02-03 inst/moto.Rmd
typo

(in figure \@ref(fig:dotchartlogmot) observe that the bottom-ranked
player, Lecuona, has a ML strength of zero but the estimate is
slightly positive for numerical reasons).

>>>>

(in figure \@ref(fig:dotchartlogmoto
) observe that the bottom-ranked
player, Lecuona, has a ML strength of zero but the estimate is
slightly positive for numerical reasons).
